A Trio of 40 to 50 Million Year Old Mini-Neptunes from Kepler, TESS, and Gaia

### 2022-04-05 papers/ms.tex
update ms

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Kepler Mini-Neptunes in Cep-Her}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of open cluster dispersal.
  Here we present an analysis of a group 
  stars spanning Cepheus ($l=100^\circ$) to Hercules
  ($l=40^\circ$), hereafter the Cep-Her complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in a sub-component of the
  Cep-Her complex called the $\delta$\ Lyr\ cluster
  \citep{bouma_kep1627_2022}.
  Here we focus on the former three systems, which are in other
  sub-components of the complex.
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 is in a dense
  sub-cluster of the complex called RSG-5, and is $46^{+9}_{-7}$\,Myr old.
  KOI-7368 and KOI-7913 are in a diffuse region that we call
  CH-2, and are $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, all three are
  most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets therefore empirically
  demonstrate that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for the black, gray, purple, and green points
  is described in Section~\ref{subsec:members}.
  %The {\bf interactive figure} enables a few different cuts to be
  %shown.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

In the context of the existing exoplanet population, the most significant
novelty about Kepler-1643~b, KOI-7368.01, and KOI-7913 is that they have normal
mini-Neptune sizes.
More specifically, the intrinsic distribution of planet sizes measured
by Kepler peaks at $\approx 2.4\,R_\oplus$, with a valley at
1.8\,$R_\oplus$, and falling off past $\approx$3.5\,$R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.

Figure~\ref{fig:rp_period_age} shows the sizes, orbital periods, and ages of
known transiting planets, emphasizing those with precise ages.
Considering planets younger than $10^8$ years, the smallest previously
known were AU~Mic~c ($\approx3.0\pm0.2\,R_\oplus$, averaging the
results of \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).
The other transiting planets younger than $10^8$ years are much
larger, with sizes between 4 and 10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2017,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020}.

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{\today}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Mini-Neptune Trio in Cep-Her}

@@

% 208 words (250 max)
\begin{abstract}
  Stellar positions and velocities from Gaia are yielding a new and
  refined view of open cluster dispersal.
  Here we present an analysis of a group stars spanning Cepheus
  ($l=100^\circ$) to Hercules ($l=40^\circ$), hereafter the Cep-Her
  complex.
  The group includes four Kepler Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet has previously been noted to be in
  the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}, which we
  argue here is a sub-component of the Cep-Her complex.
  Here we focus on the former three systems, which are in other
  sub-components of the complex.
  Based on kinematic evidence from Gaia, stellar rotation periods from
  TESS, and spectroscopy, these three systems are also $\approx$40
  million years old.
  More specifically, we find that Kepler-1643 is in a dense
  sub-cluster of the complex called RSG-5, and is $46^{+9}_{-7}$\,Myr old.
  KOI-7368 and KOI-7913 are in a diffuse region that we call
  CH-2, and are $36^{+10}_{-8}$\,Myr old.
  Based on the transit shapes and high resolution imaging, all three are
  most likely planets, with false positive probabilities of
  $6\times10^{-9}$, $4\times10^{-3}$, and $1\times10^{-4}$ for
  Kepler-1643, KOI-7368, and KOI-7913 respectively.
  These planets therefore empirically
  demonstrate that mini-Neptunes with sizes of $\approx$2 Earth
  radii exist at ages of $\approx$40 million years.
\end{abstract}

@@

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.99\textwidth]{f1.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
  {\bf Positions and velocities of candidate members of the Cep-Her
  complex.}
  {\it Top row}: On-sky positions in galactic coordinates.  Black
  points are stars for which group membership is more secure than for
  gray points.
  Kepler-1627 is in the outskirts of the $\delta$ Lyr cluster
  \citep{bouma_kep1627_2022}, which is centered at $\{ l, b\} \approx
  \{ 66^\circ, 12^\circ\}$.
  {\it Middle row}: Galactic positions.  The Sun is at $\{X, Y, Z\} =
  \{0, 0, 20.8\}$\,pc; lines of constant heliocentric distance are
  shown between 250 and 400\,pc, spaced by 50\,pc.
  {\it Bottom row}: Galactic tangential velocities (left) and
  galactic longitudinal velocity versus galactic longitude (right).
  The gray band in the lower-right shows the $\pm$1-$\sigma$
  projection of the Solar velocity with respect to the local standard
  of rest.  There is a strong spatial and kinematic overlap between
  Kepler-1643 and RSG-5 (magenta).  The local population
  of candidate young stars around KOI-7368 and KOI-7913 is more
  diffuse -- we call this region ``CH-2'' (lime-green).
  The selection method for the black, gray, purple, and green points
  is described in Section~\ref{subsec:members}.
	\label{fig:XYZvtang}
	}
\end{figure*}

@@

Current thinking about the origins and evolution of lose-in
mini-Neptunes has recently been reviewed by \citet{bean_nature_2021}.
In the context of the existing exoplanet population, the most
significant novelty about Kepler-1643~b, KOI-7368.01, and KOI-7913 is
that they have normal sizes.
More specifically, the size distribution of mini-Neptunes spans
$\approx$1.8\,$R_\oplus$ to $\approx$3.6\,$R_\oplus$, with a peak at
$\approx 2.4\,R_\oplus$ \citep[][Figure~7]{Fulton_et_al_2017}.
Figure~\ref{fig:rp_period_age} shows the sizes, orbital periods, and ages of
known transiting planets, emphasizing those with precise ages.
Considering planets younger than $10^8$ years, the smallest previously
known were AU~Mic~c ($\approx3.0\pm0.2\,R_\oplus$, averaging the
results of \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).
The other transiting planets younger than $10^8$ years are much
larger, with sizes between 4 and 10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2017,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020}.

%TODO: I think we might need James Owen to contribute something
%similar to the TOI-1227 models?
{\bf Run some evolutionary models, make some comments about the core
mass, KH timescale, etc}.
